---
title: "New to R"
output: html_document
---


**Download the latest version of R from the [Comprehensive R Archive Network](https://cran.rstudio.com/)** (CRAN). [R](https://www.r-project.org/about.html) is a programming language built for statistical analysis.

**Download [R Studio](https://www.rstudio.com/products/rstudio/#Desktop)** which is an [IDE](https://en.wikipedia.org/wiki/Integrated_development_environment) built for R. While you can use R without R Studio, R Studio makes life much better.


# Introduction resources

If you are new to R I suggest reading through [**before we start**](http://www.datacarpentry.org/R-ecology-lesson/00-before-we-start.html) and [**intro to R**](http://www.datacarpentry.org/R-ecology-lesson/01-intro-to-R.html). 

[**R for Data Science**](http://r4ds.had.co.nz/) by Hadley Wickham is a fantastic R textbook.

You might find [STOR 390](https://idc9.github.io/stor390/) helpful.

# Swirl

[**swirl**](http://swirlstats.com/) is an interactive R tutorial. Install and load the swirl package. Run the following code in the R Studio console.

```{r swirl, eval=F}
install.packages('swirl')
library(swirl)
```

Once the swirl package has loaded you can get started by running
```{r start, eval=F}
swirl()
```

There are a few swirl courses. I suggest getting started with `R Programming` which comes preloaded. You can install other courses

```{r install, eval=FALSE}
install_course("Exploratory_Data_Analysis")
install_course("Getting_and_Cleaning_Data")
install_course("Data_Analysis")
```

Once you have installed a course it should show up on the swirl dashboard.



